A graph-based approach for interactive evolutionary computation

### 2017-01-17 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
A little more Intro

\section{Introduction}
Interactive Evolutionary Algorithms (IEAs): are standard EAs whose
fitness evaluations are performed by persons with in an interactive 
system.  Thus, the main loop of the EA need a human intervention for
the quality assessment of each proposed solution. These systems have an
inherent drawback araising from the very nature of the model, namely,
the human fatigue caused by the interaction. Some authors have already
tried to address this basic problem \cite{Frade:2010:EvoGAMES}.
nevertheless, IEAs have demonstrated their ability for effectively
producing art and design \cite{Bentley:1999:intro,Sims:1991,todd:1992},.
as well as other domains \cite{ie1}.

,
\subsection{Subsection Heading Here}
Subsection text here.
\cite{Sims:1991}

>>>>

\section{Introduction}
Interactive Evolutionary Algorithms (IEAs): are standard EAs whose
fitness evaluations are performed by persons with in an interactive 
system.  Thus, the main loop of the EA needs the intervention of a
human for the quality assessment of each proposed solution. These
systems have an inherent drawback araising from the very nature of 
the algorithm, namely, the human fatigue caused by the interaction. 
Some authors have already tried to address this basic problem \cite{Frade:2010:EvoGAMES}.
nevertheless, IEAs have demonstrated their ability for effectively
producing art and design \cite{Bentley:1999:intro,Sims:1991,todd:1992},
as well as other products in many other domains \cite{ie1}. 
Several IEC have been developed as web based systems \cite{picbreeder,Musart},
depending on volunteers who visit the system to interactibly help
with the seach.

\subsection{Subsection Heading Here}
Subsection text here.,
\cite{Sims:1991}
